\documentclass{article}
\usepackage[english]{babel}

%%%%%%%%%% Start TeXmacs macros
\newcommand{\tmem}[1]{{\em #1\/}}
\newcommand{\tmstrong}[1]{\textbf{#1}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
%%%%%%%%%% End TeXmacs macros

\begin{document}

{\tmstrong{\begin{center}
  READINGS ON MATHEMATICAL PHYSICS
\end{center}}}
\begin{itemize}
  \item Gregory L. Naber,~{\tmem{Topology, Geometry and Gauge Fields:
  Foundations}}, Springer, Berlin, 1997.
  
  \item Chris Isham,~{\tmem{Modern Differential Geometry for Physicists}},
  World Scientific Press, Singapore, 1999.
  
  \item John C. Baez and Javier P. Muniain,~{\tmem{Gauge Fields, Knots and
  Gravity}}, World Scientific Press, Singapore, 1994. (My favorite, for some
  reason. For this class you just need chapters I.2-I.4 and II.1-II.2.)
  
  \item Harley Flanders,~{\tmem{Differential Forms with Applications to the
  Physical Sciences}}, Dover, New York, 1989. (Everyone has to learn
  differential forms eventually, and this is a pretty good place to do it.
  Plus, Dover books are cheap!)
  
  \item Charles Nash and Siddhartha Sen,~{\tmem{Topology and Geometry for
  Physicists}}, Academic Press, 1983. (This emphasizes the physics
  motivations... it's not quite precise at points.)
  
  \item Mikio Nakahara,~{\tmem{Geometry, Topology, and Physics}}, A. Hilger,
  New York, 1990. (More advanced.)
\end{itemize}
\begin{itemize}
  \item Herbert Goldstein, Charles Poole, and John Safko,~{\tmem{Classical
  Mechanics}}, Addison Wesley, San Francisco, 2002.
\end{itemize}
\begin{itemize}
  \item Vladimir I. Arnold,~\tmtextit{Mathematical Methods of Classical
  Mechanics}, translated by K. Vogtmann and A. Weinstein, 2nd edition,
  Springer, Berlin, 1989.
\end{itemize}

\end{document}
